Semantic Patches

### 2010-06-18 papers/MIPS2010/abstract.tex
* Just move the abstract in a clean space to clarify my ideas. :)
git-svn-id: http://gasp.dev.regis-gianas.com/svn/trunk@99 403e655e-980a-47bd-8c60-1ee5348bb6b7

We want to design a \emph{language of patches}, able to represent
% TODO changer le nom?
these transformations and their semantic properties, thus capturing
local changes in programs, as well as their global effect on the whole
project. We can see this goal as a refinement of the former idea of
``dependency''.

>>>>

We want to design a \emph{language of patches}, able to represent
% TODO changer le nom?
these transformations and their semantic properties, thus capturing
local syntactic changes in programs (the abstract syntax tree), as
well as their global effect on the whole project (the typing
derivations). We can see this goal as a refinement of the former idea
of ``dependency''.
